\chapter*{Introduction}
\addcontentsline{toc}{chapter}{Introduction}

Hello and welcome to the SAGA manual. This is my attempt to write up most of what I know about running SAGA, from my experience in various role on the committee.

When I joined SAGA, our committee was entirely new. Few (if any) of us had held any club organisation roles before, and we had several bad years before we found our feet. Hopefully, you'll never find yourself with an entirely new committee and no one to call on for help --- but if you do, maybe this manual can help you.

I've divided the manual into four main sections:

In \textbf{roles}, I talk about the roles of the committee members in SAGA. Each committee member's role isn't set in stone, but what I've suggested in here is what I've found works.

In \textbf{events}, I discuss the various sorts of events and happenings the SAGA committee will be involved with. This includes an extensive section on running a convention, as well as bureaucratic hoops such as affiliation and the like.

In \textbf{assets}, I list the various things the club owns and what you should do to keep them up-to-date and maintained.

Finally, in \textbf{documents} I have attached a couple of sample documents that you can copy for your own purposes.

This manual is by no means a finished product. As the years pass I expect that details about the club will change as new roles get added, old ones removed, and the purpose and requirements of the club change. I have supplied this manual to the club in PDF format, but have the original file (in \LaTeX) on my computer. If you want to alter this file to add your own comments, feel free to either send me your additions, or email and request the source files of the manual. You should be able to contact me (for the foreseeable future) at \texttt{jan@1klb.com}.

I would like to thank Rose Nichols for helping me write about the accounting/finance side of the club, which I never went into. I also wish to acknowledge all those who've been on committee with me through the years, and Robert Urquhart, who acted as general guide and regent while us newbies found our feet running this thing.

I hope you find this guide helpful, and the club flourishes under your rule.

\vspace{3em}

\hfill Jan-Yves Ruzicka

\hfill August 2013