\section{Website}

The SAGA website, hosted at http://www.saga.org.nz, is our main web presence and the best way for new members to find out information about the club. It's currently running the Wordpress blogging engine, which allows us to host static pages (\eg for events or general information) as well as a blog for keeping members abreast of big events.

Wordpress is relatively easy to maintain - almost everything is done via an admin back-end, and the main thing that requires a bit of savvy is backing everything up. I recommend backing up the website \textit{at least} yearly. Wordpress has decent instructions on their site on how to back up a wordpress blog.

Posts (\ie dated entries on the blog) and pages (\ie static pages used for reference) can be created, edited and maintained through the admin backend. For more complicated stuff, google is your friend, or other SAGA members may be able to help.

It is officially the job of the Promotions Officer to keep the website up-to-date, but in previous years the Promotions Officer has not necessarily felt comfortable maintaining a website. For this reason the committee may designate someone else in charge of the website. It's generally a good idea that someone be in charge of the website. Whoever it is, they should get the admin username and password from the last person in charge of the website. They may wish to change the admin password for security reasons, and they can then add, edit or remove other profiles as required.