\section{Changing the club rules}
\label{sec:rulechanges}

Sometimes you want to change the rules of the club. Maybe you find a loophole, or someone does something you never expected to happen, or maybe by the time you read this 50\% of the club are uploaded intelligences outsourced to a mainframe in Singapore.

The point being, the rules will need to change from time to time. This is how you do that.

\subsection{Aside: nomenclature}

While the club's rules are often referred to as a constitution throughout this document, the Societies Office calls them ``rules''. The terms are used interchangeably in this section.

\subsection{Proposing a rule change}

Any club member may propose a change to the rules, but they need to jump through a few hoops. These hoops are detailed in articles 5.1--5.5 of the club's rules, see Section~\ref{sec:constitution}.

In order to propose a change to the rules, you must:

\begin{itemize}
  \item Make the proposal at a general meeting. You can either do it at the AGM, or ask the committee to hold an SGM (see article 7.1).
  \item Announce your changes to the club and the president at least seven days before the meeting.
\end{itemize}

At the meeting, you need at least 75\% of the attending members to vote for your change. If they vote for it, congratulations! But your fun isn't over yet.

\subsection{Changing the rules}

Now you have new rules, I suggest typing up a nice copy and putting it somewhere for the club members to read. The website is a good place to put this\footnote{http://www.saga.org.nz/club-details/constitution}, but you may also want a copy in the committee Dropbox or other file store.

If you wish to get this document updated, see the introduction on how to contact me and get a revised copy.

\subsection{Notifying people}

It's good manners, but not required, to notify the UCSA about rules changes. Occasionally they will have problems with rules, and it's better you find out now than when they reject your request for affiliation.

You must also notify the Societies Office of your change. This is detailed on their website\footnote{http://www.societies.govt.nz/cms/incorporated-societies/running-a-society/how-do-you-change-the-rules-of-a-society}.